Regular singular Volterra equations on complex domains

### 2023-08-07 reg-sing-volterra.tex
Revise statement of lem:perturbed_volterra
Propose revisions to the text around the statement too.

We'll prove this result in Section~\ref{sec:proto-construction-regularity}, Proposition~\ref{prop:asymptotic at infinity}.

\begin{lemma}\label{lem:perturbed_volterra}
Let $g$ be a function in the space $\in\singexp{\sigma+\epsilon}{A}(\Omega)$ defined in Section~\ref{fn-spaces}. The Volterra equation
\[ f = \Big[\hardpart +\softpart \Big] f + g \]
given by an operator of the kind described in Sections \ref{setting:basic} and \ref{setting:perturbed}, admits a unique solution $f$ that belongs to $\singexp{\sigma+\epsilon}{\Lambda}(\Omega)$, for every $\Lambda\geq A$ \textcolor{magenta}{[check]}. 
\end{lemma}

We'll prove this result in Section~\ref{sec:V is a contraction}: in Proposition \ref{prop:get-contraction} we construct the functions space where $\volterra$ is a contraction. Then the result follows by the contraction mapping theorem.

\begin{thm}\label{thm:general_volterra}
    Assume $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}, \eqref{cond:slow}} and {\em \eqref{cond:diag-basic}} from Section \ref{setting:basic}. Assume $\softpart$ satisfies {\em Condition \eqref{cond:eps-lambda}} from Section \ref{setting:perturbed}. Then the Volterra equation 
    \[f = \left[ \hardpart + \softpart \right] f\]
    admits a unique solution in the affine subspace
\[ f_0 + \singexpalg{\tau-1+\epsilon}(\Omega) \]
of the function space $\singexpalg{\tau-1}(\Omega)$, defined in Section~\ref{fn-spaces}. The function $f_0$ is the prototypical solution of \eqref{eqn:test_solution} and it belongs to the function space $\singexp{\tau-1}{\lambda_0}(\Omega)$.
\end{thm}

We'll prove this result in Sections~\ref{sec:existence and uniqueness}: using Proposition \ref{prop:smoothing} we show that $\softpart$ maps the prototype solution into a more regular function space. Then the result follows as a consequence of Lemma \ref{lem:perturbed_volterra}.

%%\begin{thm}
%%Let $\Omega$ be an acute-angled sector around $0$ in the complex plane. \textcolor{DarkTurquoise}{I don't think it's really necessary for $\Omega$ to have a sharp point at $0$, but the condition of being an acute-angled sector is sufficient and easy to state.}

%%Consider a Volterra operator
%%\[ \mathcal{V} = p + \partial^{-1} \circ q + \mathcal{R} \]
%%over $\Omega$ which can be decomposed, as shown above, into the sum of a zeroth-order part $p$, a first-order part $\partial^{-1} \circ q$, and an effectively higher-order part $\mathcal{R}$. To be precise, $\mathcal{R}$ is supposed to be an integral operator of the form
%%\[ [\mathcal{R}\varphi](a) = \int_{\zeta = 0}^{a} k(a, \cdot)\,\varphi\,d\zeta \]
%%which is effectively finite-order over $\Omega$ in the sense of Definition~\ref{fin-order}, with order at least $1 + \epsilon$ for some $\epsilon \in (0, \infty)$.

%%Assume, furthermore, that:
%%\begin{itemize}
%%\item There's some $c \in (0, \infty)$ for which
%%$|p(a)| \lesssim e^{c|\zeta(a)|}$ and $|q(a)| \lesssim e^{c|\zeta(a)|}$ over all $a \in \Omega$.
%%\item $p$ and $q$ extend holomorphically over $\zeta = 0$.
%%\item $p$ has a simple zero at $\zeta = 0$.
%%\end{itemize}
%%Let $p_1$ and $q_0$ be the values of $\tfrac{\partial}{\partial \zeta} p$ and $q$, respectively, at $\zeta = 0$.

%%Under these conditions, let's try to solve the regular singular Volterra equation
%%\[ \mathcal{V}f = 0. \]
%%The leading-order part of the equation,
%%\[ \big[p_1 \zeta + \partial^{-1} \circ q_0\big]f = 0, \]
%%has $\zeta^{\tau-1}$ as a solution, where $\tau = p_1/q_0$. If we guess that the function spaces defined in Section~\ref{fn-spaces} are well suited for this problem, we might hope for the full equation to have a solution of the form
%%\[ f = \zeta^{\tau-1} + f_*, \]
%%where $f_* \in \holoL{\infty, 1-\tau-\epsilon}_Z(\Omega)$ for some $Z \in \C$. When $Z\Omega$ is in the right half-plane and $|Z|$ is large enough, there is in fact a unique solution of this form.
%%\end{thm}

\subsection{Acknowledgements}

>>>>

We'll prove this result in Section~\ref{sec:proto-construction-regularity}, Proposition~\ref{prop:asymptotic at infinity}.
\begin{thm}\label{thm:general_volterra}
In the perturbed operator $\volterra = \hardpart +\softpart$ from Section~\ref{setting}, suppose the prototypical part $\hardpart$ satisfies Conditions \eqref{cond:sing}, \eqref{cond:slow}, and \eqref{cond:diag-basic} from Section~\ref{setting:basic}, and the perturbation $\softpart$ satisfies Condition \eqref{cond:eps-lambda} from Section~\ref{setting:perturbed}. Then the Volterra equation
\[f = \volterra f\]
has a unique solution $f$ in the affine subspace
\[ f_0 + \singexpalg{\tau-1+\epsilon}(\Omega) \]
of the function space $\singexpalg{\tau-1}(\Omega)$ defined in Section~\ref{fn-spaces}. Here, $f_0$ is the prototype solution \eqref{eqn:test_solution} from Theorems \ref{thm:basic_volterra}--\ref{thm:proto-growth}, which belongs to the function space $\singexp{\tau-1}{\lambda_0}(\Omega)$. For any $\rho > \tau$, the uniqueness of the solution still holds in the larger affine subspace $f_0 + \singexpalg{\rho-1}(\Omega)$.
\textcolor{RoyalBlue}{Assume $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}, \eqref{cond:slow}} and {\em \eqref{cond:diag-basic}} from Section \ref{setting:basic}. Assume $\softpart$ satisfies {\em Condition \eqref{cond:eps-lambda}} from Section \ref{setting:perturbed}. Then the Volterra equation 
\[f = \left[ \hardpart + \softpart \right] f\]
admits a unique solution in the affine subspace
\[ f_0 + \singexpalg{\tau-1+\epsilon}(\Omega) \]
of the function space $\singexpalg{\tau-1}(\Omega)$, defined in Section~\ref{fn-spaces}. The function $f_0$ is the prototypical solution of \eqref{eqn:test_solution} and it belongs to the function space $\singexp{\tau-1}{\lambda_0}(\Omega)$.}
\end{thm}
\textcolor{RoyalBlue}{We'll prove this result in Sections~\ref{sec:existence and uniqueness}: using Proposition \ref{prop:smoothing} we show that $\softpart$ maps the prototype solution into a more regular function space. Then the result follows as a consequence of Lemma \ref{lem:perturbed_volterra}.}\par
%--------
This result will follow from a more general result about inhomogeneous equations.
\begin{lemma}\label{lem:perturbed_volterra}
In the perturbed operator $\volterra = \hardpart +\softpart$ from Section~\ref{setting}, suppose the prototypical part $\hardpart$ satisfies Conditions \eqref{cond:sing}, \eqref{cond:slow}, and \eqref{cond:diag-basic} from Section~\ref{setting:basic}, and the perturbation $\softpart$ satisfies Condition \eqref{cond:eps-lambda} from Section~\ref{setting:perturbed}. Suppose we're also given a function $g$, which for some $\rho > \tau$ belongs to the space $\singexpalg{\rho-1}(\Omega)$ defined in Section~\ref{fn-spaces}. Then the inhomogeneous Volterra equation
\[ f = \volterra f + g, \]
has a unique solution $f$ in the space $\singexpalg{\rho-1}(\Omega)$.

\textcolor{RoyalBlue}{Let $g$ be a function in the space $\in\singexp{\sigma+\epsilon}{A}(\Omega)$ defined in Section~\ref{fn-spaces}. The Volterra equation
\[ f = \Big[\hardpart +\softpart \Big] f + g \]
given by an operator of the kind described in Sections \ref{setting:basic} and \ref{setting:perturbed}, admits a unique solution $f$ that belongs to $\singexp{\sigma+\epsilon}{\Lambda}(\Omega)$, for every $\Lambda\geq A$ \textcolor{magenta}{[check]}.}
\end{lemma}
\textcolor{RoyalBlue}{We'll prove this result in Section~\ref{sec:V is a contraction}: in Proposition \ref{prop:get-contraction} we construct the functions space where $\volterra$ is a contraction. Then the result follows by the contraction mapping theorem.}\par
%---------
We will prove Lemma~\ref{lem:perturbed_volterra} in Sections \ref{sec:V is a contraction}--\ref{sec:existence and uniqueness}, using the contraction mapping theorem. The heart of the argument is Proposition~\ref{prop:get-contraction}, which shows us how to find relevant subspaces where $\volterra$ is a contraction.

We will reduce Theorem~\ref{thm:general_volterra} to Lemma~\ref{lem:perturbed_volterra} in Section~\ref{sec:existence and uniqueness}, by rewriting the homogeneous equation we want to solve as an inhomogeneous equation in a more regular function space. To show that the inhomogeneous term, $\softpart f_0$, is regular enough, we use Proposition~\ref{prop:smoothing} from Section~\ref{sec:image under soft_part} to show that $\softpart$ improves on the regularity of $f_0$ described by Theorem~\ref{thm:proto-growth}.

%%To prove Theorem~\ref{thm:general_volterra}, we will rewrite the homogeneous equation we want to solve as an inhomogeneous one, with $\softpart f_0$ as the inhomogeneous term.

%%We will reduce Theorem~\ref{thm:general_volterra} to Lemma~\ref{lem:perturbed_volterra} in Section~\ref{sec:existence and uniqueness}, with the help of Proposition~\ref{prop:smoothing} from Section~\ref{sec:image under soft_part}, which can be used to show that $\softpart f_0$ is regular enough to serve as the inhomogeneous term in the lemma.
\subsection{Acknowledgements}
